---
title: "Homework 1"
author: "Yiman Rui"
date: "2026-09-25"
output: github_document
---

Libraries:
```{r}
library(tidyverse)
```

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains measurements of penguins from three species: `r paste(unique(penguins$species), collapse = ",")`, observed on the islands: `r paste(na.omit(unique(penguins$island)), collapse = ",")`. Other important numeric variables include bill length, bill depth, flipper length, body mass, and year. 

The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

Plots:
```{r}
penguins_plot =
  ggplot(
    penguins,
    aes(
      x = bill_length_mm,
      y = flipper_length_mm,
      color = species
    )
  ) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  )

penguins_plot
```
```{r}
ggsave(
  "penguins_scatterplot.png",
  plot = penguins_plot,
)
```

