---
title: "Homework 1"
author: "Yiman Rui"
date: "2026-09-25"
output: github_document
---

Libraries:
```{r}
library(tidyverse)
```

## Problem 1
```{r}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains measurements of penguins from three species: `r paste(unique(penguins$species), collapse = ",")`, observed on the islands: `r paste(na.omit(unique(penguins$island)), collapse = ",")`. Other important numeric variables include bill length, bill depth, flipper length, body mass, and year. 

The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

Plots:
```{r}
penguins_plot =
  ggplot(
    penguins,
    aes(
      x = bill_length_mm,
      y = flipper_length_mm,
      color = species
    )
  ) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species"
  )

penguins_plot
```
```{r}
ggsave(
  "penguins_scatterplot.png",
  plot = penguins_plot,
)
```

## Problem 2
```{r}
set.seed(8105)

df =
  tibble(
    random_sample = rnorm(10),
    sample_positive = random_sample > 0,
    character_vector = c(
      "a", "b", "c", "d", "e",
      "f", "g", "h", "i", "j"
    ),
    factor_vector = factor(
      c(
        "A", "B", "C", "A", "B",
        "C", "A", "B", "C", "A"
      )
    )
  )

df
```

Mean of each variables:
```{r}
mean(pull(df, random_sample))
mean(pull(df, sample_positive))
mean(pull(df, character_vector))
mean(pull(df, factor_vector))
```

The mean can be calculated for the numeric and logical variables, but
not for the character or factor variables. The numeric variable contains
quantitative values so it has a meaningful mean. For the logical
variable, R treats `TRUE` as 1 and `FALSE` as 0, so its mean represents
the proportion of observations that are `TRUE`. Character and factor
variables represent non-numeric information, so their means are not
directly meaningful.
